\documentclass[]{article}

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\begin{document}

\title{User Guide}
\date{}
\maketitle
\tableofcontents


\section{Installation}

\subsection{External Softwares}

\begin{itemize}
\item Linux
\begin{itemize}
\item \textbf{cLapack:} install liblapacke-dev (it’s also available in synaptic package manager)
\item \textbf{ATLAS: } \textit{sudo apt-get install libatlas-base-dev}

\item  \textbf{SuiteSparse: } 

\begin{itemize}
\item \textit{sudo apt-get install build-essential} (If Linux is freshly installed and it does not have g++)
\item Download Suitesparse unzip it and go to home folder. 
\item change directory of terminal to home folder 
\item  \textit{make library} 

\item \textit{sudo make install }
\end{itemize}

\end{itemize}

\item Mac : 
\begin{itemize}
\item \textbf{SuiteSparse: } Follow the read me file provided with SuiteSparse. 
\end{itemize}
\end{itemize}
\section{Generating a problem and compiling in c}
\begin{enumerate}
\item \textbf{Adding a path: } Download alternative-direction-toolbox.  Open the matlab and add “alternative-direction-toolbox/split” folder to matlab path.

\item \textbf{Define a problem in MATLAB: } 

\begin{itemize}
\item \textbf{For Mac: } change matlab path to “alternative-direction-toolbox/split/test/testSplitCoder” and  open the 	file “testSplitCoder.m”. Define a problem there. For reference, different constraints and different  algorithms are illustrated with comments.

\item \textbf{For Linux: } change matlab path to “alternative-direction-toolbox/split/test/testLinux” and  open the file “testSplitCoder.m”.  For the reference different constraints and different  algorithms are illustrated with comment.
\end{itemize}

\item \textbf{Code and data generation: }  Once the problem is defined in m file (use testSplitCoder.m as a template) run the file and it will solve the optimisation problem in matlab. It will also create file called probdata.c and probate.h in the current matlab path.

\item \textbf{For linux only: }   

\begin{itemize}
 \item  delete \#include “accelerate.h” from the probate.h 
\item  add following lines in probdata.h file. 

\begin{itemize}
\item                                 \#include “clapack.h” 
\item				 \#include”cblas.h” 
\item				\# include “clapack\_mac.h”
\item				\#include “lapacke.h” 
\end{itemize}
\end{itemize}

\item Enter the following 2 command in terminal to compile.

\begin{itemize}
\item \textit{make clean }
\item \textit{make}
\end{itemize}
\end{enumerate} 


\section{Selecting Linear Algebra Packages: }

\subsection{Linear Solver: }

\subsubsection{SuiteSparse: }

\subsubsection{cLAPACK: }

\subsubsection{Library free computation: }

\subsection{Matrix Vector Multiplication: }
\subsubsection{SuiteSparse: }

\subsubsection{cLAPACK: }

\subsubsection{Library free computation: }


\end{document}